What makes musicians infer teaching intentions?

### 2022-04-08 experiment-1/analysis/analysis.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
```

@@

ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + geom_vline(xintercept = 188, linetype="dotted", color = "gray", size = 1)
```

@@

ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

@@

ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

@@

ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

>>>>

ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1)
```

@@

ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
```

@@

ggscatter(cv, x = "CV", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "CV", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1)
```

@@

ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1)
```

@@

ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1)
```

### 2022-04-08 experiment-2/analysis/analysis.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

@@

ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100)
```

>>>>

ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1)
```

@@

ggscatter(ioi_tra, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme(aspect.ratio = 1)
```

@@

ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + 
scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1)
```

### 2022-04-08 paper/manuscript.Rmd
update figures
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r ioi-1, include = FALSE}
cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) + theme_pubr(base_size = 20, base_family = "Helvetica")
cor_ioi_1

# save
ggsave(here("paper/image", "cor_ioi_1.png"), plot = cor_ioi_1, dpi = 600, width = 7, height = 5)
img_cor_ioi_1 <- image_read(here("paper/image", "cor_ioi_1.png"))
```

@@

```{r kot-1, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica")
cor_kot_1

# save
ggsave(here("paper/image", "cor_kot_1.png"), plot = cor_kot_1, dpi = 600, width = 7, height = 5)
img_cor_kot_1  <- image_read(here("paper/image", "cor_kot_1.png"))
```

@@

```{r vel-1, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica")
cor_vel_1

# save
ggsave(here("paper/image", "cor_vel_1.png"), plot = cor_vel_1, dpi = 600, width = 7, height = 5)
img_cor_vel_1  <- image_read(here("paper/image", "cor_vel_1.png"))
```

@@

```{r vel-diff-1, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica")
cor_vel_diff_1

# save
ggsave(here("paper/image", "cor_vel_diff_1.png"), plot = cor_vel_diff_1, dpi = 600, width = 7, height = 5)
img_cor_vel_diff_1  <- image_read(here("paper/image", "cor_vel_diff_1.png"))
```

@@

```{r ioi-2, include = FALSE}
cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica")
cor_ioi_2

# save
ggsave(here("paper/image", "cor_ioi_2.png"), plot = cor_ioi_2, dpi = 600, width = 7, height = 5)
img_cor_ioi_2 <- image_read(here("paper/image", "cor_ioi_2.png"))
```

@@

```{r kot-2, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica")
cor_kot_2

# save
ggsave(here("paper/image", "cor_kot_2.png"), plot = cor_kot_2, dpi = 600, width = 7, height = 5)
img_cor_kot_2  <- image_read(here("paper/image", "cor_kot_2.png"))
```

@@

```{r vel-2, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_2 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + xlim(50, 102) + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica")
cor_vel_2

# save
ggsave(here("paper/image", "cor_vel_2.png"), plot = cor_vel_2, dpi = 600, width = 7, height = 5)
img_cor_vel_2  <- image_read(here("paper/image", "cor_vel_2.png"))
```

@@

```{r vel-diff-2, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_2 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + ylim(0, 100) +
  theme_pubr(base_size = 20, base_family = "Helvetica")
cor_vel_diff_2

# save
ggsave(here("paper/image", "cor_vel_diff_2.png"), plot = cor_vel_diff_2, dpi = 600, width = 7, height = 5)
img_cor_vel_diff_2  <- image_read(here("paper/image", "cor_vel_diff_2.png"))
```

>>>>

```{r ioi-1, include = FALSE}
cor_ioi_1 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(150, 242, 20)) + coord_cartesian(xlim = c(150, 242), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_ioi_1.png"), plot = cor_ioi_1, dpi = 300, width = 6, height = 6)
img_cor_ioi_1 <- image_read(here("paper/image", "cor_ioi_1.png"))
```

@@

```{r kot-1, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_1 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-250, 200, 100)) + coord_cartesian(xlim = c(-250, 200), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 20, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_kot_1.png"), plot = cor_kot_1, dpi = 300, width = 7, height = 5)
img_cor_kot_1  <- image_read(here("paper/image", "cor_kot_1.png"))
```

@@

```{r vel-1, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_1 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 20, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_vel_1.png"), plot = cor_vel_1, dpi = 300, width = 7, height = 5)
img_cor_vel_1  <- image_read(here("paper/image", "cor_vel_1.png"))
```

@@

```{r vel-diff-1, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_1 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-35, 55, 20)) + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_vel_diff_1.png"), plot = cor_vel_diff_1, dpi = 300, width = 7, height = 5)
img_cor_vel_diff_1  <- image_read(here("paper/image", "cor_vel_diff_1.png"))
```

@@

```{r ioi-2, include = FALSE}
cor_ioi_2 <- ggscatter(ioi, x = "Mean", y = "Teaching", color = "Skill", add = "reg.line", palette = "d3",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "IOIs (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(240, 332, 20)) + coord_cartesian(xlim = c(240, 332), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_ioi_2.png"), plot = cor_ioi_2, dpi = 300, width = 6, height = 6)
img_cor_ioi_2 <- image_read(here("paper/image", "cor_ioi_2.png"))
```

@@

```{r kot-2, include = FALSE}
kot_all$Subcomponent <- factor(kot_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_kot_2 <- ggscatter(kot_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE,
          xlab = "KOT (ms)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-300, 150, 100)) + coord_cartesian(xlim = c(-300, 150), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_kot_2.png"), plot = cor_kot_2, dpi = 300, width = 7, height = 5)
img_cor_kot_2  <- image_read(here("paper/image", "cor_kot_2.png"))
```

@@

```{r vel-2, include = FALSE}
vel_all$Subcomponent <- factor(vel_all$Subcomponent, levels = c("Legato", "Staccato", "Forte", "Piano"))
cor_vel_2 <- ggscatter(vel_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity (0-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(40, 100, 10)) + coord_cartesian(xlim = c(40, 100), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_vel_2.png"), plot = cor_vel_2, dpi = 300, width = 7, height = 5)
img_cor_vel_2  <- image_read(here("paper/image", "cor_vel_2.png"))
```

@@

```{r vel-diff-2, include = FALSE}
vel_diff_all$Subcomponent <- factor(vel_diff_all$Subcomponent, levels = c("LtoS", "StoL", "FtoP", "PtoF"))
cor_vel_diff_2 <- ggscatter(vel_diff_all, x = "Mean", y = "Teaching", color = "Subcomponent", add = "reg.line", palette = "d3", facet.by = "Skill",
          add.params = list(fill = "lightgray"), conf.int = TRUE, cor.coef = FALSE,
          xlab = "Velocity Difference (-127-127)", ylab = "Judged as teaching (%)") + scale_x_continuous(breaks = seq(-40, 55, 20)) + coord_cartesian(xlim = c(-40, 55), ylim = c(0, 100)) + theme(aspect.ratio = 1) + theme_pubr(base_size = 18, base_family = "Helvetica")

# save
ggsave(here("paper/image", "cor_vel_diff_2.png"), plot = cor_vel_diff_2, dpi = 300, width = 7, height = 5)
img_cor_vel_diff_2  <- image_read(here("paper/image", "cor_vel_diff_2.png"))
```
